%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Sirjan Kafle's Resume

% Template Credit:
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{format}


\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Sirjan}{Kafle}{ \urlstyle{same}\url{http://sirjank.github.io} \\
\href{mailto:sxkafle12@gmail.com}{sxkafle12@gmail.com} | 972-900-2931
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection[University of California Berkeley]{\texorpdfstring{University of \\ California Berkeley}{University of California Berkeley}}
\descript{Electrical Engineering and Computer Science}
\location{Expected May 2018 | Berkeley, CA}
College of Engineering \\
\location{ Cum. GPA: 3.93 / 4.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/SirjanK}{\custombold{SirjanK}} \\
LinkedIn://  \href{https://www.linkedin.com/in/sirjankafle}{\custombold{sirjankafle}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Computer Science}
CS189 - Machine Learning \\
CS170 - Efficient Algorithms \\
CS162 - Operating Systems and Systems Programming \\
CS176 - Algorithms for Computational Biology \\
CS186 - Database Systems \\
CS61C - Machine Structures \\
CS61B - Data Structures \\
CS70 - Discrete Math and Probability Theory \\
CS61A - Structure and Interpretation of Computer Programs
\sectionsep

\subsection{EE \& Mathematics}
EECS126 - Probability and Random Processes \\
EECS127 - Optimization Models and Applications \\
Math104 - Real Analysis \\
Math54 - Linear Algebra \& Differential Equations \\
Math53 - Multivariable Calculus \\
EE16A/B - Designing Information Devices and Systems 1 \& 2

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Programming}
\location{Languages}
Java \textbullet{}   Python \textbullet{} C \textbullet{} Scala \textbullet{} Pig \textbullet{} JavaScript  \textbullet{} SQL \\
\location{Tools/Platforms}
Android \textbullet{} Hadoop \textbullet{} TensorFlow \textbullet{} Flask \textbullet{} Gradle \textbullet{} HTML \textbullet{} CSS \textbullet{} Bash Scripting \\
\location{Other}
Git \textbullet{} UNIX \textbullet{} LaTeX
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{LinkedIn}
\descript{Machine Learning \& Relevance Engineer Intern}
\location{May 2017 - Aug 2017 | Mountain View, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Modeled and Engineered own project on the Feed Relevance team to realize new efforts put in place by the team.
\item Lifted relevant metrics associated with the team through the project and set groundwork for further experiments.
\item Worked with TensorFlow to build models and big data platforms like Hadoop to investigate and prepare large datasets.
\end{tightemize}
\sectionsep

\runsubsection{HERE}
\descript{Highly Autonomous Driving Software Intern}
\location{June 2016 – Jan 2017 | Berkeley, CA}
\begin{tightemize}
\item Built an Android Surface Application to communicate with various pieces of hardware using the Robot Operating System Java library.
\item Facilitated data collection for creating Maps to aid Autonomous Driving efforts.
\item Worked under the Agile system with daily standups, frequently showcasing features personally implemented to stakeholders.
\end{tightemize}
\sectionsep

\runsubsection{Mobile Developers of Berkeley}
\descript{Product Manager}
\location{August 2015 - Current | Berkeley, CA}
\begin{tightemize}
\item Led an Android team to build a medical application for an outside client. 
\item Acted as PM and Software Architect, collaborating with the client on feature requests and cross platform compatibility, as well as building with the team.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Personal Projects}
\runsubsection{WireFly}
\location{CalHacks Capital One Prize Winner}
\begin{tightemize}
\item Developed a Web App to simulate optimal peer-to-peer network for international money transfers.
\item Modeled a graph network for money transfers all across the world as a Linear Program, on which the Simplex algorithm was run.
\item Employed real data on transfer rates and used the Capital One API to create accounts in a variety of countries to create a complicated network.
\end{tightemize}
\sectionsep

\runsubsection{LocServ}
\location{Raspberry Pi Application in Python}
\begin{tightemize}
\item Wrote a Local Flask Server hosted using Ngrok as a Webhook for the Twilio API to send and receive terminal commands via SMS messages.
\item Ran the commands synchronously on the Raspberry Pi (although compatible with other Linux machines) and sent output back to user.
\item Scripted Python and Bash commands in order to generate a seamless method for setting up the Server and configuring the webhook.
\end{tightemize}
\sectionsep

\runsubsection{Qlic Android Application}
\location{Social Media Transmission App}
\begin{tightemize}
\item Designed and developed an Android Application dealing with sharing information with surrounding groups. 
\item Used the Google Nearby API for transferring string payloads and dealt with custom serialization and deserialization.
\end{tightemize}
\sectionsep

\runsubsection{Concentraid Android Application}
\location{Student Study Aid App}
\begin{tightemize}
\item Engineered an Android Application for breaking up study time based on the Pomodoro Effect.
\item Used open source libraries dealing with various specialized Views and adopted a system of Callbacks for managing tasks.
\end{tightemize}
\end{minipage} 
\end{document}  \documentclass[]{article}
